The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems

### 2011-10-08 shortRange.inhomo/writeDown/main.tex
backup, add converge.new

\documentclass[aps,pre,preprint]{revtex4}
% \documentclass[aps,pre,twocolumn]{revtex4}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

Heterogeneous systems, in which density (or atom type) changes within
the length scale of several molecules, are more universal than
homogeneous systems in nature. However, the direct molecular
simulation of heterogeneous systems by the cut-off method will
encounter non-trival difficulties that do not exist in the homogeneous
system simulations.  The simulation results are found to converge only
at a very large cut-off radius value~\cite{duque2004some,
  ismail2007application}, also denpend on the energy/force continuity
at the cut-off and the way of applying the long-range
correction~\cite{trokhymchuk1999computer, shen2007comparative,
  guo1997long, mecke1997molecular, janecek2006long, goujon2004monte}.
Therefore, it is necessary to systemetically study the precision of
the short-range interaction calculation, and to develop methods
screening out the aforementioned cut-off artifect in the heterogeneous
systems.

@@

In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
component) by the red solid line. The $y$ and $z$ components are not
shown because their magnitudes are negligible.  On the left interface,
the correction force is along the positive direction of $x$ axis,
namely poiting right.  On the right interface, the correction force is
of the same maganitude but poiting left. Therefore, the liquid density
should be higher and the vapor density should be lower than the
corresponding uniform cut-off simulation.  The real error (in green
square) and the estimated homogeneity error (in blue solid line) are
all presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows
the homogeneity error across the simulation region, which implies the
contribution of the heterogeneity error is successfully removed, or is
at least negligible. In the bulk liquid region, the homogeneity error
is slightly overestimated, which is the same as the uniform and
adaptive cut-off simulations.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
  \caption{The convergence of the equilibrium gas and liquid density
    with respect to the cut-off radius. All densities are substracted
    by the reference value, namely, the liquid and vapor density
    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
    presents the results of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
    method. }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
  \caption{The convergence of the surface tension with respect to the
    cut-off radius.  This figure presents the results of three
    methods, namely the uniform cut-off (URC), the adaptive cut-off
    (ARC) and the force correction (FC) method.  The results with and
    without heterogeneous pressure correction (HPC) are shown together
    for comparison. The reference surface tensions, shown by solid
    black lines, are measured by the uniform cut-off method with
    $r_c^\ast=13$ using HPC.}
  \label{fig:tmp6}
\end{figure}

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to increasing cut-off radius. The red, green
and blue points with error bars denote the results of uniform,
adaptive and long-range force correction, respectively.
In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
gas densities are connected by the dashed lines, and the liquid
densities are connected by the solid lines to guide the eyes.  In
Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
points connected by the dashed lines) are presented with pressure
corrected surface tension (data points connected by solid lines) and
the reference surface tension measured by uniform cut-off simulations
at $r_c^\ast = 13$ with pressure correction.

@@

For all temperatures studied, the liquid and gas densities of the
uniform and the adaptive cut-off methods are almost identical at the
same cut-off radius. This observation is also true for the surface
tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
larger homogeneous force error in the bulk liquid/gas regions will not
disturb the accuracy of the equilibrium densities and surface tension.
The adaptive cut-off method roughly saves one half of the
computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
adaptive cut-off depends on the property of the system: if the bulk
regions dominate the system, and the density difference between the
bulk regions is big enough to produce large error in the interfacial regions,
then the adaptive cut-off will save a lot of
computational expense. On the other hand, if the interfacial region is
computationally intensive, the adaptive cut-off will not improve the efficency
greatly.

For the liquid/vapor densities, the long-range force correction method
presents a much better convergence than the uniform and adaptive
cut-off simulations. The properties perfectly converge when the cut-off
radius is equal to or larger than 5, and the convergence at a cut-off
as small as 3.5 is acceptable.  With the same cut-off radius, the
computational cost of the force correction is nearly the same as the
uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
time, the force accuracy is more than one order of maganitude better.
% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.

With the long-range pressure correction, the convergence of the
surface tension of all methods are greatly improved. The discrepancy
between the corrected and uncorrected pressure is the value of the
correction, which decreases with increasing cut-off radius. However,
even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
uncertainty gets larger, and better convergence is achieved at smaller
cut-off radius.

Comparing the results of the force correction method at
$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
force accuracy of the former method is 3--5 times worse than the later
(see Tab. \ref{tab:tmp1}), however, the
density and surface tension accuracies are comparable to and
sometimes even better than the later (see Fig. \ref{fig:tmp5} and
\ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the above observation
indicates different errors play different roles in the simulations.
The homogeneity error is actually the variation of the corrected error
force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
implies that the corrected error force may point to any direction with
the same probability, and may be cancelled by itself in a long time
average.  The heterogeneity error, in contrast, stems from the
non-vanishing value of the mean error force, which is alway pointing
at one certain direction (the same direction as the low-to-high
density jump), and has no oppotunity to be self-cancelled.

@@

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the long-range
    force correction (LFC) method.
    The computational cost is the number of pairwise interaction 
    measurements, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

@@

>>>>

\documentclass[aps,pre,preprint]{revtex4-1}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

Heterogeneous systems, in which density (or atom type) changes within
the length scale of several molecules, are more universal than
homogeneous systems in nature. However, the direct molecular
simulation of heterogeneous systems by the cut-off method will
encounter non-trival difficulties that do not exist in the homogeneous
system simulations.  The simulation results are found to converge only
at a very large cut-off radius value~\cite{duque2004some,
  ismail2007application}, also denpend on the energy/force continuity
at the cut-off and the way of applying the long-range
correction~\cite{trokhymchuk1999computer, guo1997long,
  mecke1997molecular, janecek2006long, goujon2004monte,
  shen2007comparative}.  Therefore, it is necessary to systemetically
study the precision of the short-range interaction calculation, and to
develop methods screening out the aforementioned cut-off artifect in
the heterogeneous systems.

@@

In Fig. \ref{fig:tmp4}, the red solid line presents the $x$ component
correction force that is calculated every 40 time steps. The $y$ and
$z$ components are not shown because their magnitudes are negligible.
On the left interface, the correction force is along the positive
direction of $x$ axis, namely poiting right.  On the right interface,
the correction force is of the same maganitude but poiting
left. Therefore, the liquid density should be higher and the vapor
density should be lower than the corresponding uniform cut-off
simulation.  The real error (in green square) and the estimated
homogeneity error (in blue solid line) are all presented in
Fig. \ref{fig:tmp4}.  Cleary, the real error follows the homogeneity
error across the simulation region, which implies the contribution of
the heterogeneity error is successfully removed, or is at least
negligible. In the bulk liquid region, the homogeneity error is
slightly overestimated, which is the same as the uniform and adaptive
cut-off simulations.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.gas.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.liquid.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.85.gas.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.85.liquid.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.gas.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.liquid.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.gas.eps} 
  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.liquid.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.70.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.10.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.20.eps} 
  \caption{The convergence of the equilibrium gas and liquid densities
    with respect to the cut-off radius. All densities are compared
    with the refence value (black solid line), namely, the liquid and
    vapor densities meansured with a uniform cut-off radius
    $r_c^\ast=13$. The gray region denotes the statistcal uncertainty
    of the reference value.  This figure presents the results of three
    methods, namely the uniform cut-off (URC), the adaptive cut-off
    (ARC) and the force correction (LFC) method. }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.20.eps} 
  \caption{The convergence of the surface tension with respect to the
    cut-off radius.  This figure presents the results of three
    methods, namely the uniform cut-off (URC), the adaptive cut-off
    (ARC) and the long-range force correction (LFC) method.  The
    results with and without long-range pressure correction (LPC) are
    shown together for comparison. The reference surface tensions,
    shown by solid black lines, are measured by the uniform cut-off
    method with $r_c^\ast=13$ using LPC.}
  \label{fig:tmp6}
\end{figure}

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the long-range
    force correction (LFC) method.
    The computational cost is the number of pairwise interaction 
    measurements, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{LFC} & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{LFC} & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{LFC} & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{LFC} & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{LFC} & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{LFC} & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{LFC} & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{LFC} & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{LFC} & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
    &     &\textrm{LFC} & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{LFC} & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{LFC} & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to increasing cut-off radius. The red, green
and blue points with error bars denote the results of uniform,
adaptive and long-range force correction, respectively.  In
Fig. \ref{fig:tmp5}, all densities are compared with the reference
value measured by uniform cut-off simulations of $r_c^\ast = 13$, with
the statistcal uncertainty denoted by the gray region. The densities
are connected by the the solid lines to guide the eyes.  In
Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
points connected by the dashed lines) are presented with pressure
corrected surface tension (data points connected by solid lines).  The
reference surface tension is measured by uniform cut-off simulations
at $r_c^\ast = 13$ with long-range pressure correction.

@@

For all temperatures studied, the liquid and gas densities of the
uniform and the adaptive cut-off methods are almost identical at the
same cut-off radius, see Fig. \ref{fig:tmp5}. This observation is also
true for the surface tension, see Fig. \ref{fig:tmp6}. This indicates
that controlling the maximum of force error (see Tab. \ref{tab:tmp1})
and introducing larger homogeneous force error in the bulk liquid/gas
regions will not disturb the accuracy of the equilibrium densities and
surface tension.  The adaptive cut-off method roughly saves one half
of the computational cost (see Tab. \ref{tab:tmp1}). The benefit of
the adaptive cut-off depends on the property of the system: if the
bulk regions dominate the system, and the density difference between
the bulk regions is big enough to produce large error in the
interfacial regions, then the adaptive cut-off will save a lot of
computational expense. On the other hand, if the interfacial region is
computationally intensive, the adaptive cut-off will not improve the
efficency greatly.

For the liquid/vapor densities, the long-range force correction method
presents a much better convergence than the uniform and adaptive
cut-off simulations. The properties converge when the cut-off radius is
only 3.5.  With the same cut-off radius, the computational cost of the
force correction is nearly the same as the uniform cut-off methods,
see Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is
more than one order of maganitude better.
% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.
We also observe that the liquid densities are systemetically higher
than the reference results. This fact will be discussed later by
comparing with literature results.

The surface tension result of the force correction without pressure
correction is slightly better than the uniform and adaptive cut-off
methods with out pressure correction, see Fig. \ref{fig:tmp6}.  With
the help of the long-range pressure correction, the convergence of the
surface tension of all methods are greatly improved.  The force
correction method converges at $r_c^\ast = 3.5$, and the
uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0$ ($T^\ast
= 0.70$) and at $r_c^\ast = 7.5$ ($T^\ast = 0.85,\ 1.10,\ 1.20$).  The
discrepancy between the corrected and uncorrected tension is the
amount of the correction, which decreases with increasing cut-off
radius. However, even at $r_c^\ast=10$, the correction is not
negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
temperature, amount of correction is sometimes smaller than the
statistcal uncertainty.

We list in Tab. \ref{tab:comparison} a wide range of results reported
by literature~\cite{janecek2006long, lotfi1992vapour,
  errington2003evaluating, ismail2007application}, as well as our
uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
results for comparison. The abbreviations in the table are explained
in the caption. The MC/LEC, MD/Ewald and our methods are direct
simulation of the heterogeneous system. The MD/Npt+test particle and
MC/GC-TMMC methods are simulation of homogeneous systems that do not
have the difficulties of heterogeneity, and are believed to be more
precise than direct simulations~\cite{shen2007comparative}.
\begin{table}
  \centering
  \caption{Equilibrium densities and surface tension comparision 
    with various literature results: Monte Carlo with long-range
    energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
    particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
    grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
    molecular dynamics with dispersion term calculated by the Ewald
    summation (MD/Ewald)~\cite{ismail2007application}
    and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
    proposed by this work. The surface tensions of this work are
    corrected by the long-range pressure correction.
    The cut-off radius of the Ewald summation is for the real space.
  }
  \label{tab:comparison}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
  % \begin{tabular}{cccc|cccc}\hline\hline
    $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
    0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
    0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
    0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
    0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
    0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
    0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
    0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
    0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
    0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
    0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
    0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
    1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
    1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
    1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
    1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
    1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
    1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
    1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
    1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
    1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
    1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(06) & this work\\
    1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
    \hline\hline
  % \end{tabular}
  \end{tabular*}
\end{table}

Comparing the results of the force correction method at
$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
force accuracy of the former method is 3--5 times worse than the later
(see Tab. \ref{tab:tmp1}), however, the
density and surface tension accuracies are comparable to and
sometimes even better than the later (see Fig. \ref{fig:tmp5} and
\ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the above observation
indicates different errors play different roles in the simulations.
The homogeneity error is actually the variation of the corrected error
force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
implies that the corrected error force may point to any direction with
the same probability, and may be cancelled by itself in a long time
average.  The heterogeneity error, in contrast, stems from the
non-vanishing value of the mean error force, which is alway pointing
at one certain direction (the opposite direction of the density
gradient), and has no oppotunity to be self-cancelled.

@@

@@

In this paper, we developed the force error estimate for non-bonded
short-range interaction in the heterogeneous system.
